---
title: "Logos"
author: "jcb"
date: "12 septembre 2015"
output: html_document
---

Logos pour la cartographie
==========================

Dossier Trame_Commune/Logos

Les logos sont préférentiellement au format .png

source: 

- ambulances: http://www.flaticon.com/free-icons/ambulance_225
- hélicos: http://www.flaticon.com/search/helicopters
- hospitals: http://www.flaticon.com/free-icon/hospital-buildings_33777
- SAMI, SDIS: http://www.flaticon.com/free-icon/male-telemarketer_81523
- déconta: http://www.flaticon.com/free-icon/man-showering_76657
- sang: http://www.flaticon.com/free-icon/blood-perfusion_69691

Licence: Icon made by [Freepick](http://www.flaticon.com/authors/freepik) from www.flaticon.com 

Le dossier __Logos/data__ contient un certain nombre d'images à difféents niveaux de résolution:

- ambulance15
- shopper5 (hélicoptère)
- hospital11
- man253 (douche mobile)
- men39 (douche fixe)
- perfusion
- transport51 (ambulance)

Afficher une image PNG dans un graphe
-------------------------------------

- source: http://stackoverflow.com/questions/4975681/r-creating-graphs-where-the-nodes-are-images
- source: https://ryouready.wordpress.com/2014/09/12/using-colorized-png-pictograms-in-r-base-plots/
```{}
library(png)
img <- readPNG(system.file("img", "Rlogo.png", package="png"))
# une zone graphique
plot(c(100, 250), c(300, 450), type = "n", xlab = "", ylab = "")

rasterImage(img, 150, 300, 200, 350, interpolate = TRUE)
rasterImage(img, 100, 400, 110, 410, angle = 90, interpolate = TRUE)

file <- "rat.png"
rat <- readPNG(file)
rasterImage(rat, 100, 400, 134, 428, interpolate = TRUE)

```

Ambulance
---------

```{r}
library(png)
# amb <- readPNG("Logos/data/transport51(8).png")
amb <- readPNG("data/transport51(8).png")
class(amb)
dim(amb)

```
L'objet __amb__ est un tableau numérique de 64 lignes et 64 colonnes avec quatre couches (red, green, blue, alpha; short RGBA).

Let’s have a look at the first layer (red) and replace all non-zero entries by a one and the zeros by a dot. This will show us the pattern of non-zero values and we already see the contours.

```{r}
l4 <- amb[,,1]
l4[l4 > 0] <- 1
l4[l4 == 0] <- "."
d <- apply(l4, 1, function(x) {
 cat(paste0(x, collapse=""), "\n") 
})
```
To display the image in R one way is to raster the image (i.e. the RGBA layers are collapsed into a layer of single HEX value) and print it using rasterImage.

```{r}
rimg <- as.raster(amb) # raster multilayer object
r <- nrow(rimg) / ncol(rimg) # image ratio
plot(c(0,10), c(0,10), type = "n", xlab = "", ylab = "", asp=1) # une zone graphique vide
rasterImage(rimg, 0, 0, 1, r) # img, x1, y1, x2, y2
rasterImage(rimg, 5, 2, 6, 3)

smur <- as.raster(readPNG("data/ambulance15(14).png"))
rasterImage(smur, 4, 2, 5, 3)
rasterImage(smur, 6, 4, 8, 6)
```

